On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2024-07-17 manuscript/manuscript.tex
tex: update graphicspath for reproducibility

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-used.pdf}
    \caption{Fraction of hourly demand met with carbon-free electricity.}
    \label{fig:10-2025-IE-p1-used}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Portfolio capacity procured by participating consumers.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_capacity.pdf}
        \label{fig:10-2025-IE-p1-ci_capacity}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{Cost breakdown of a procurement policy.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_costandrev.pdf}
        \label{fig:10-2025-IE-p1-ci_costandrev}
    \end{subfigure}
    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
    \label{fig:10-2025-IE-p1-ci_procurement}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (w/ \gls{ldes}).}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p2-ci_costandrev.pdf}
        \label{fig:10-2025-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy \\
        (w/ \gls{ldes} and advanced technologies).}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p3-ci_costandrev.pdf}
        \label{fig:10-2025-IE-p3-ci_costandrev}
    \end{subfigure}
    \caption{The breakdown of costs per procurement policy if participating consumers have an access to a wider palette of technologies: w/ \gls{ldes} (left panel); w/ \gls{ldes} and advanced clean firm generators (right panel).
    }
    \label{fig:10-2025-IE-p23-ci_procurement}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers (Germany).}
        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_emisrate.pdf}
        \label{fig:10-2025-DE-p3-ci_emisrate}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers (Poland).}
        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_emisrate.pdf}
        \label{fig:10-2025-PL-p3-ci_emisrate}
    \end{subfigure}

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Germany).}
        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-zone_emissions.pdf}
        \label{fig:10-2025-DE-p3-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Poland).}
        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-zone_emissions.pdf}
        \label{fig:10-2025-PL-p3-zone_emissions}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (Germany).}
        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_costandrev.pdf}
        \label{fig:10-2025-DE-p3-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (Poland).}
        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_costandrev.pdf}
        \label{fig:10-2025-PL-p3-ci_costandrev}
    \end{subfigure}
    \caption{Selected results for scenarios when participating consumers are located in Germany (left) and Poland (right); all plots are for technological palette~3.}
    \label{fig:10-2025-DEPL-p3-4plots}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Fraction of hourly demand met with carbon-free electricity.}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-used.pdf}
        \label{fig:10-2030-IE-p1-used}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_emisrate.pdf}
        \label{fig:10-2030-IE-p1-ci_emisrate}
    \end{subfigure}

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \caption{Cost breakdown of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy: technological palette~2.}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p2-ci_costandrev.pdf}
        \label{fig:10-2030-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy: technological palette~3.}
        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p3-ci_costandrev.pdf}
        \label{fig:10-2030-IE-p3-ci_costandrev}
    \end{subfigure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/used.pdf}
    \caption{Fraction of hourly demand met with carbon-free electricity.}
    \label{fig:10-2025-IE-p1-used}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Portfolio capacity procured by participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
        \label{fig:10-2025-IE-p1-ci_capacity}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{Cost breakdown of a procurement policy.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p1-ci_costandrev}
    \end{subfigure}
    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
    \label{fig:10-2025-IE-p1-ci_procurement}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (w/ \gls{ldes}).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy \\
        (w/ \gls{ldes} and advanced technologies).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p3-ci_costandrev}
    \end{subfigure}
    \caption{The breakdown of costs per procurement policy if participating consumers have an access to a wider palette of technologies: w/ \gls{ldes} (left panel); w/ \gls{ldes} and advanced clean firm generators (right panel).
    }
    \label{fig:10-2025-IE-p23-ci_procurement}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers (Germany).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_emisrate.pdf}
        \label{fig:10-2025-DE-p3-ci_emisrate}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers (Poland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_emisrate.pdf}
        \label{fig:10-2025-PL-p3-ci_emisrate}
    \end{subfigure}

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Germany).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
        \label{fig:10-2025-DE-p3-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Poland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
        \label{fig:10-2025-PL-p3-zone_emissions}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (Germany).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_costandrev.pdf}
        \label{fig:10-2025-DE-p3-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy (Poland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_costandrev.pdf}
        \label{fig:10-2025-PL-p3-ci_costandrev}
    \end{subfigure}
    \caption{Selected results for scenarios when participating consumers are located in Germany (left) and Poland (right); all plots are for technological palette~3.}
    \label{fig:10-2025-DEPL-p3-4plots}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Fraction of hourly demand met with carbon-free electricity.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/used.pdf}
        \label{fig:10-2030-IE-p1-used}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2030-IE-p1-ci_emisrate}
    \end{subfigure}

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \caption{Cost breakdown of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy: technological palette~2.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p2/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Cost breakdown of a procurement policy: technological palette~3.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p3/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p3-ci_costandrev}
    \end{subfigure}
